**NeuroKit2: A Python Toolbox for Neurophysiological Signal Processing**

### 2020-09-08 paper/manuscript_v4.Rmd
typo in researchgap2
version release

<!-- Research gap 2 -->
Additionally, psychology and neuroscience face a "reproducibility crisis" [@topalidou2015long; @open2015estimating; @milkowski2018replicability; @maizey2019barriers] which has lead to a profound reassessment of research practices (by researchers, publishers, fund agencies, ...).
The opacity of data processing, such as ill-specified, or incaccessible analysis pipelines, plays a major role in the crisis.
This issue could in part be alleviated by making analyses code an integral part of scientific publications, rather than treating a paper as the sole and most important part of the research  project. However, distributing the analysis script alongside the paper poses new challenge:
Scripts must be shareable (not always feasible with closed-source and proprietary software or programming languages), accessible (well-documented and organized scripts) and reproducible (which is inherently difficult for software relying on a graphical user interfaces - GUI - in which the manual point-and-click sequence is hard to automate).

@@

In this section, we present two examples that illustrate the most common use-cases. The first example shows how to extract the characteristics of physiological activity during a certain time interval (not necessarily tied to a specific and sudden event). The second example presents an event-related paradigm, in which the interest lies in shorter-term physiological changes related to specific events (see **Figure 1** and **Table 1**). The example datasets are available with the package and can be downloaded using the `data()` function. This utility reads comma separated values files (*.csv*) with Pandas dedicated function (*pd.read_csv()*), where each column is a different biosignal. Both examples' results are generated using the 0.0."" version release of *NeuroKit2*.

>>>>

<!-- Research gap 2 -->
Additionally, psychology and neuroscience face a "reproducibility crisis" [@topalidou2015long; @open2015estimating; @milkowski2018replicability; @maizey2019barriers] which has lead to a profound reassessment of research practices (by researchers, publishers, fund agencies, ...).
The opacity of data processing, such as ill-specified, or inaccessible analysis pipelines, plays a major role in the crisis.
This issue could in part be alleviated by making analyses code an integral part of scientific publications, rather than treating a paper as the sole and most important part of the research  project. However, distributing the analysis script alongside the paper poses new challenge:
Scripts must be shareable (not always feasible with closed-source and proprietary software or programming languages), accessible (well-documented and organized scripts) and reproducible (which is inherently difficult for software relying on a graphical user interfaces - GUI - in which the manual point-and-click sequence is hard to automate).

@@

In this section, we present two examples that illustrate the most common use-cases. The first example shows how to extract the characteristics of physiological activity during a certain time interval (not necessarily tied to a specific and sudden event). The second example presents an event-related paradigm, in which the interest lies in shorter-term physiological changes related to specific events (see **Figure 1** and **Table 1**). The example datasets are available with the package and can be downloaded using the `data()` function. This utility reads comma separated values files (*.csv*) with Pandas dedicated function (*pd.read_csv()*), where each column is a different biosignal. Each row is a sample that correspond to signals' value at a given time interval. Both examples' results are generated using the 0.0.""<!--SPECIFY RELEASE-->" version release of *NeuroKit2*.
